Inferring Graphics Programs from Images

### 2017-05-06 paper.tex
description of neural architecture

\begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

%  \node at (canvas.x,canvas.y) {Canvas};

\end{tikzpicture}

>>>>

We developed a deep network architecture for efficiently inferring a
execution trace, $T$, from an image, $I$.  Our model constructs the
trace one drawing command at a time.  When predicting the next drawing
command, the network takes as input the target image $I$ as well as
the rendered output of previous drawing commands.  Intuitively, the
network looks at the image it wants to explain, as well as what it has
already drawn.  It then decides either to stop drawing or proposes
another drawing command to add to the execution trace; if it decides
to continue drawing, the predicted primitive is rendered to its
``canvas'' and the process repeats.

Figure~\ref{architecture} illustrates this architecture.  We first
pass the target image and a rendering of the trace so far to a
convolutional network. Given the features extracted by the
convolutionional network, a multilayer perceptron then predicts a
distribution over the next drawing command to add to the trace.  We
predict the drawing command token-by-token, and condition each token
both on the image features and on the previously generated tokens.
For example, the network first decides to emit the \verb|CIRCLE| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|CIRCLE|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|CIRCLE| token, and the
$x$ coordinate.

The distribution over the next drawing command factorizes:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta [t_k | f_\theta(I,\text{render}(T)), \{t_j\}_{j = 1}^{k - 1}]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $T$ is an execution trace, $\theta$ are the
parameters of the neural network, and $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network). The distribution over
execution traces factorizes as:
\begin{equation}
  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
\end{equation}
where $|T|$ is the length of execution trace $T$, and the \verb|STOP|
token is emitted by the network to signal that the execution trace
explains the image.

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR. When we
have the generative model (the rendering function), we need not solve
an unsupervised or reinforcement learning problem.

\begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
\end{tikzpicture}
